Unreliable heterogeneity: how measurement error obscures heterogeneity in meta-analyses in psychology

### 2023-06-17 manuscript/manuscript.qmd
pdf figures

knitr::include_graphics("../figures/manuscript/flowchart-simulation-design.png")
```

@@

```{r Figure 2, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/manuscript/z-r-hs-plot.png")
```

@@

```{r Figure 3, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/manuscript/r_tau_0.02-0.08.png")
```

@@

```{r Figure 4, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/manuscript/sample_size.png")
```

>>>>

knitr::include_graphics("../figures/manuscript/flowchart-simulation-design.pdf")
```

@@

```{r Figure 2, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/manuscript/z-r-hs-plot.pdf")
```

@@

```{r Figure 3, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/manuscript/r_tau_0.02-0.08.pdf")
```

@@

```{r Figure 4, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/manuscript/sample_size.pdf")
```
